WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-14 paper/ms.tex
updated paper to include Spitzer times

\begin{abstract}
  %TODO: final numbers
  By combining data from the Transiting Exoplanet Survey Satellite
  (TESS) with data from previous studies, we show that the transit
  times of WASP-4b are incompatible with a constant orbital period.
  The transits observed by TESS occurred $77.8 \pm 10.8$~seconds
  earlier than one would expect, based on the previous data.  The
  orbital period appears to be shrinking by $\dot{P}=-12.1 \pm 1.2$
  milliseconds per year.   A simple clock offset is unlikely, because
  TESS observations of other hot Jupiters (WASP-6b, 18b, and 46b) are
  compatible with a constant period and rule out a 77.8-second offset
  at the 6.3$\sigma$ level.  The timing variations seem to be
  astrophysical, and could be caused by apsidal precession, or perhaps
  by tidal decay.  The latter seems implausible on theoretical
  grounds, as it would require a stellar quality factor $Q_\star'
  \approx 3\times10^4$.  Apsidal precession would imply an
  eccentricity $e\approx1.6\times 10^{-3}$, and the possibility of
  measuring the planet's Love number.  A Doppler shift from WASP-4's
  acceleration towards us could account for at most one quarter of the
  observed period change (at $2\sigma$).  Further observations are
  needed to confirm and understand the timing variation.
\end{abstract}

@@

The TESS spacecraft recorded images of WASP-4 in an $11\times11$ pixel
array every 2 minutes.   The data were downlinked via the Deep Space
Network, and the Payload Operations Center then converted the
timestamps from the spacecraft clock to TESS Julian Day in the {\it
Temps Dynamique Barycentrique} (TDB) reference.  The data were then
processed through the Science Processing Operations Center (SPOC)
pipeline at NASA Ames~\citep{jenkins_tess_2016}.  SPOC used the known
spacecraft trajectory to compute the barycentric time corrections on a
target by target basis, and reported timestamps in ``BTJD'', where
${\rm BTJD} = {\rm BJD} - 2457000$, BJD is the barycentric julian
date, and all times are in the TDB reference (see
\citealt{urban_explanatory_2012} for explanations of time systems).
The lightcurves were then vetted and released by the MIT TESS Science
Office to the Mikulski Archive for Space
Telescopes~\citep{ricker_tess_alerts_2018}.

@@

After ``cleaning'' the data, we normalized the flux measurements by
dividing out the median flux.  We converted the timestamps from BTJD
to BJD by adding the appropriate 2457000 day offset
\citep{tess_data_product_description_2018}.  Many of these and
subsequent processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018} We opted not to
``flatten'' the lightcurves at this stage, as is often done with {\it
e.g.}, a spline or gaussian process regression.  Such procedures are
asymmetric about the transit minimum and can skew the transit time
measurement without being captured by the measurement uncertainties.

@@

Having defined the free and fixed parameters, we calculated an initial
guess for the free parameters by maximizing the likelihood.  We then
sampled over the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.
Table~1 gives the results, which are in reasonable agreement with the
parameters reported by \citet{gillon_improved_2009},
\citet{southworth_high-precision_2009}, and
\citet{huitson_gemini_2017}.

To measure mid-transit times, we then focused on each individual
transit window.  We fit for a model transit, plus a local linear
trend.  We allowed four free parameters per transit: the time of
mid-transit $t_{\rm tra}$, the planet-to-star radius ratio, and the
slope and intercept of the line.  We fixed the remaining
parameters~---~$a/R_\star$, $i$, $P$, and the limb-darkening
coefficients~---~to the best-fit values determined from the
phase-folded TESS lightcurve.

After completing an initial fit for each transit, we set the
photometric error bars to equal the standard deviation of the
out-of-transit points of the residual lightcurve.  We then reperformed
the fitting procedure, using the empirically determined photometric
errors.

@@

Figure~\ref{fig:lightcurves} shows the lightcurves, best-fit models,
and residuals.  Table~2 reports the mid-transit times and their
uncertainties.
Binning the residuals to 1-hour windows and taking the median absolute
deviation, the lightcurves have an RMS of $586\,{\rm ppm}\,{\rm
hr}^{1/2}$.  The predicted\footnote{\url{github.com/lgbouma/tnm}}
photon-counting noise is $410\,{\rm ppm}\,{\rm hr}^{1/2}$.  At
$T\approx11.8$, with a 9-pixel aperture read noise is expected to
contribute an additional $202\,{\rm ppm}\,{\rm hr}^{1/2}$ in
quadrature.  The predicted zodiacal background contribution is
$673\,{\rm ppm}\,{\rm hr}^{1/2}$, based on the
\citet{winn_photonflux_2013} model, which \citet{Sullivan_2015} used
in planet detection simulations.  This zodiacal noise prediction seems
to have been an overestimate, given the observed RMS of WASP-4.  A
broader assessment of TESS's photometric performance is beyond
the scope of this work.

@@

We compute the bolometric flux using broadband magnitudes from
available all-sky catalogs, as follows: $G$ from {\it Gaia\/} DR2,
$B_T V_T$ from {\it Tycho-2}, $BVgri$ from {\it APASS}, $JHK_S$ from {\it
2MASS}, and the {\it WISE}~1--4 passbands, thus spanning the
wavelength range 0.4--22~$\mu$m.  Combining the implied angular radius
with the {\it Gaia} DR2 parallax, and adjusting for the parallax
offset \citep{stassun_evidence_2018}, we obtain the stellar radius.
For the stellar mass, we started with the $a/R_\star$ value found from
the phase-folded TESS lightcurve.  The implied stellar density follows
\citep{seager_unique_2003}, and using the stellar radius we obtain the
semi-major axis and stellar mass.  We get the planet radius using our
measured $R_{\rm p}/R_\star$.  Finally, for the planet mass we use the
observed RV semi-amplitude and inclination angle from the transit
\citep{triaud_spin-orbit_2010}.

We list the resulting parameters in Table~3, and adopt them for the
remaining analysis.  Our parameters broadly agree with those of previous
authors
\citep{wilson_wasp-4b_2008,gillon_discovery_2009,winn_transit_2009,southworth_homogeneous_2011,petrucci_no_2013}.
% The sole exception is that our measured $R_{\rm p}/R_\star$ value is
% slightly smaller than most ground-based measurements (see Tables 2 and
% 3 of \citealt{hoyer_tramos_2013}).  However, looking at the I-band
% measurements of \citet{hoyer_tramos_2013} and taking the mean + std
% deviation, it's a ~1 sigma effect. So I won't mention it!
Comparing our empirical result with the Yonsei-Yale evolutionary track
predicted by the spectroscopic parameters, we see that WASP-4 has an
age $\approx 7\,{\rm Gyr}$, and is securely in the main-sequence stage
of evolution.

@@

\begin{figure*}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.9\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Timing residuals and best-fit models for WASP-4b.}
        Points are observed transit times minus a linear fit to all
        observed times.  Less precise times are more transparent.  The
        best constant period model (gray line) is a poor fit to the
        observations.  The best-fit tidal decay model (blue) and
        apsidal precession model (orange) can fit the data.  The
        binned TESS point (star) is for display purposes only.
        \label{fig:times}
    }
\end{figure*}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=0.40\textwidth]{f4.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf WASP-4b has a short eccentricity damping time and a medium
    decay time compared to other hot Jupiters.  It seems to orbit a
    main sequence host.
    }
    {\bf \it Top:}
    Points are transiting giant planets from \citet{bonomo_gaps_2017},
    who measured the eccentricities using radial velocities.  Solid
    squares (including WASP-18b) have significant eccentricity
    detections.  The axes are chosen so that constant eccentricity
    damping timescales (Equation~\ref{eq:de_dt}) are lines.  The
    contours shown assume $Q_{\rm p}' = 10^5$.
    {\bf \it Middle:} 
    Axes are chosen so to that constant orbital decay timescales
    (Equation~\ref{eq:da_dt}) are lines.  The contours shown assume
    $Q_\star' = 10^7$.
    {\bf \it Bottom:}
    HR diagram highlighting WASP-12b, which shows timing variations
    similar to WASP-4b.  We also show hot Jupiters for which we
    detect no timing variation (see \S~\ref{sec:hj_verification}).
    \label{fig:context}
  }
\end{figure}

@@

To explore this possibility, we repeat the timing analysis of the main
paper, for other hot Jupiters with long preceding observing baselines.
We first checked which hot Jupiters were observed over the first two
TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}} and
TEPCat \citep{southworth_homogeneous_2011}.  We then selected hot
Jupiters for which there were at least five distinct epochs reported
in the peer-reviewed literature.  We required that each observation be
of a single transit, that the midpoint be fit as a free parameter, and
that the time system be clearly documented.  Our final hot Jupiter
sample included WASPs-4b, -5b, -6b, -18b, and -46b.  The collected and
measured times are given in Tables~5, 6, 7, and 8 for each.

Using the literature timing data for each hot Jupiter, we then
performed a least-squares fit to a linear ephemeris.  Using the
best-fit values and variances, we calculated the uncertainty on the
predicted transit time during the TESS observations.  This gave 9, 94,
18, 42, and 60 seconds for WASPs-4b, -5b, -6b, -18b, and -46b.  We
show in Figure~\ref{fig:hjs} that WASP-4b is the only hot Jupiter that
transited significantly earlier than expected.

@@

For each planet, we then ask: what fraction of the posterior for
$t_{\rm offset}$ is consistent with an offset worse than $77$ seconds?
For WASP-4b, the answer is unsurpringly about half.  For WASP-6b, the
most constraining object, about 1 sample in 2 million is consistent
with such a timing offset ($4.9\sigma$).  For WASP-18b, 1 in 63
samples would be consistent with this timing offset ($2.1\sigma$), and
in WASP-46b, the limit is 1 in 38 samples ($1.9\sigma$).  For WASP-5b,
the predicted time is too imprecise to rule out timing offsets at the
necessary amplitude.  Multiplying the three independent probabilities
for WASPs-5b, 6b, and -18b, we rule out $t_{\rm offset} < -77\ {\rm
seconds}$ at $6.3\sigma$, or about about 1 part in 5 billion.

@@

% \section{Verifying the WASP-4 Archival Times}
% \label{sec:verify_archival_times}
% 
% \begin{figure*}[ht!]
%   \begin{center}
%     \leavevmode
%     \includegraphics[width=0.9\textwidth]{f7.pdf}
%   \end{center}
%   \caption{
%     {\bf Extra times for WASP-4b neither confirm nor refute the
%     	period-decay.}
%     Our timing analysis (Section~\ref{sec:timing}) imposes stringent
%     selection criteria for lightcurves.
%     Here we overplot additional points from the Exoplanet Transit
%     Database (ETD), and the discovery epoch from \citet{wilson_wasp-4b_2008}.
%     \label{fig:verify}
%   }
% \end{figure*}
% 
% The preceding analysis shows that the TESS timestamps are consistent
% at the requisite level with the ${\rm BJD}_{\rm TDB}$ reference.
% Another explanation for the WASP-4b timing variation could be
% incorrect archival times.
% As a sanity check on the times we included for our analysis in
% Table~1, we collected times from the Exoplanet Transit Database
% \citep[ETD; ][]{poddany_ETD_2010}.  We considered only the 12
% lightcurves of the highest self-reported quality (${\rm DQ} = 1$).  We
% then inspected each lightcurve by eye.  If the lightcurve showed
% substantial red noise, we discarded it.  This left 9 midtimes,
% reported in ${\rm HJD}_{\rm UTC}$. We converted the times to ${\rm
% BJD}_{\rm TDB}$ \citep{eastman_achieving_2010}.
% 
% The resulting times are shown in Figure \ref{fig:verify}.  Focusing on
% the epochs that overlap with \citet{huitson_gemini_2017}'s study, four
% of six possible times agree with the \citet{huitson_gemini_2017}
% times; the other two fall about 90 seconds early.  With their stated
% uncertainties, these 6 ETD data points are inconsistent with a
% constant period.  The 6 points came from 5 different observers.
% Systematic errors in absolute clock offsets by different observers
% should be uncorrelated; if there were such systematic errors in the
% ETD times, this could explain the many-sigma outliers.  Though the
% majority of the reported times do support the accuracy of the
% \citet{huitson_gemini_2017} times, a systematic procedure would call
% for averaging the ETD times.  If we did this, and discarded the four
% \citet{huitson_gemini_2017} epochs, it is likely that the evidence for
% period decay would become much weaker.  Since
% \citet{huitson_gemini_2017} documented their time system clearly, and
% produced lightcurves of extremely high quality, we included their times
% in our analysis.  From private correspondence with
% \citealt{huitson_gemini_2017}, the authors also stand by their
% timestamps\todo[inline]{verify this}. Since the ETD data come from
% heterogeneous sources, their timestamps are less clearly documented,
% and the times are thus more prone to systematic errors, we
% categorically omit them from consideration.
% 
% We also overplotted the discovery epoch reported by
% \citet{wilson_wasp-4b_2008}. 
% This epoch folded together WASP-S survey data, a partial FTS
% lightcurve, and a complete EulerCam lightcurve. 
% Though not explicitly stated by \citet{wilson_wasp-4b_2008}, the
% archival WASP-S lightcurves are in ${\rm HJD}_{\rm UTC}$, so they can
% be converted to ${\rm BJD}_{\rm TDB}$ without uncertainty in the
% absolute time reference (Collier-Cameron, priv.\ comm.).
% The discovery epoch falls about 2 minutes earlier than the epochs we
% used for the fit, and is visible in the lower left of Figure
% \ref{fig:verify}.

>>>>

\begin{abstract}
  By combining data from the Transiting Exoplanet Survey Satellite
  (TESS) with data from previous studies, we show that the transit
  times of WASP-4b are incompatible with a constant orbital period.
  The transits observed by TESS occurred $81.5 \pm 11.8$~seconds
  earlier than one would expect, based on the previous data.  The
  orbital period appears to be shrinking by $\dot{P}=-12.6 \pm 1.2$
  milliseconds per year.   A simple clock offset is unlikely, because
  TESS observations of other hot Jupiters (WASP-6b, 18b, and 46b) are
  compatible with a constant period and rule out a 81.5-second offset
  at the 6.3$\sigma$ level.  The timing variations seem to be
  astrophysical, and could be caused by apsidal precession, or perhaps
  by tidal decay.  The latter seems implausible on theoretical
  grounds, as it would require a stellar quality factor $Q_\star'
  \approx 3\times10^4$.  Apsidal precession would imply an
  eccentricity $e\approx1.8\times 10^{-3}$, and the possibility of
  measuring the planet's Love number.  A Doppler shift from WASP-4's
  acceleration towards us could account for at most one quarter of the
  observed period change (at $2\sigma$).  Further observations are
  needed to confirm and understand the timing variation.
\end{abstract}

@@

The TESS spacecraft recorded images of WASP-4 in an $11\times11$ pixel
array every 2 minutes.   The data were downlinked via the Deep Space
Network. The timestamps from the spacecraft clock were then converted
by the Payload Operations Center to TESS Julian Day in the {\it
Temps Dynamique Barycentrique} (TDB) reference.  The images were then
reduced to lightcurves by the Science Processing Operations Center (SPOC)
at NASA Ames~\citep{jenkins_tess_2016}.  During this processing, SPOC used
the known
spacecraft trajectory to compute the barycentric time corrections on a
target by target basis, and reported timestamps in ``BTJD'', where
${\rm BTJD} = {\rm BJD} - 2457000$, BJD is the barycentric julian
date, and all times are in the TDB reference (\citealt{urban_explanatory_2012} 
describe the relevant time systems).
The lightcurves were then vetted and released by the MIT TESS Science
Office to the Mikulski Archive for Space
Telescopes~\citep{ricker_tess_alerts_2018}.

@@

After ``cleaning'' the data, we normalized the flux measurements by
dividing out the median flux.  We converted the timestamps from BTJD
to BJD by adding the appropriate 2457000 day offset
\citep{tess_data_product_description_2018}.  Many of these and
subsequent processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018} We did not
``flatten'' the lightcurves, as is often done with {\it
e.g.}, a spline or gaussian process regression.  Such procedures are
asymmetric about the transit minimum and can skew the midtime
measurement without being captured by the measurement uncertainties.

@@

Having defined the free and fixed parameters, %we calculated an initial
%guess for the free parameters by maximizing the likelihood.  W
we then
sampled over the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.
Table~1 gives the results, which are in reasonable agreement with the
parameters reported by {\it e.g.},
\citet{southworth_high-precision_2009} and 
\citet{huitson_gemini_2017}.

To measure the transit midtimes, we then fit  each individual transit
for a model transit, plus a local linear trend.  We allowed four free 
parameters per transit: the time of
mid-transit $t_{\rm tra}$, the planet-to-star radius ratio, and the
slope and intercept of the line.  We fixed the remaining
parameters%~---~$a/R_\star$, $i$, $P$, and the limb-darkening
%coefficients~---~
to the best-fit values determined from the
phase-folded TESS lightcurve.

After completing an initial fit for each transit, we set the
photometric error bars to equal the standard deviation of the
out-of-transit points of the residual lightcurve.  We then repeated
the fitting procedure, using the empirically determined photometric
errors.

@@

Figure~\ref{fig:lightcurves} shows the lightcurves, best-fit models,
and residuals.  Table~2 reports the mid-transit times and their
uncertainties.
Binning the residuals to 1-hour windows and taking the median absolute
deviation, the lightcurves have an RMS of $586\,{\rm ppm}\,{\rm
hr}^{1/2}$.  The predicted\footnote{\url{github.com/lgbouma/tnm}}
photon-counting noise is $410\,{\rm ppm}\,{\rm hr}^{1/2}$.  For a
$T\approx11.8$ star with a 9-pixel aperture, read noise is expected to
contribute an additional $202\,{\rm ppm}\,{\rm hr}^{1/2}$ in
quadrature.  The predicted zodiacal background contribution is
$673\,{\rm ppm}\,{\rm hr}^{1/2}$, based on the
\citet{winn_photonflux_2013} model, which \citet{Sullivan_2015} used
in planet detection simulations.  This zodiacal noise prediction seems
to have been an overestimate, given the observed RMS of WASP-4.  A
broader assessment of TESS's photometric performance is beyond
the scope of this work.

@@

We compute the bolometric flux using broadband magnitudes from
available all-sky catalogs, as follows: $G$ from {\it Gaia\/} DR2,
$B_T V_T$ from {\it Tycho-2}, $BVgri$ from {\it APASS}, $JHK_S$ from {\it
2MASS}, and the {\it WISE}~1--4 passbands, thus spanning the
wavelength range 0.4--22~$\mu$m.  Combining the implied angular radius
with the {\it Gaia} DR2 parallax, and adjusting for the parallax
offset \citep{stassun_evidence_2018}, we obtain the stellar radius.
For the stellar mass, we started with the $a/R_\star$ value found from
the phase-folded TESS lightcurve.  The implied stellar density follows
\citep{seager_unique_2003}, as do the
semi-major axis and stellar mass.  We get the planet radius using our
$R_{\rm p}/R_\star$ measurement.  Finally, for the planet mass we use the
inclination angle from the transit, and the RV semi-amplitude from 
\citet{triaud_spin-orbit_2010}.

We list the resulting parameters in Table~1, and adopt them for the
remaining analysis.  Our parameters broadly agree with those of previous
authors
\citep{wilson_wasp-4b_2008,gillon_discovery_2009,winn_transit_2009,southworth_homogeneous_2011,petrucci_no_2013}.
% The sole exception is that our measured $R_{\rm p}/R_\star$ value is
% slightly smaller than most ground-based measurements (see Tables 2 and
% 3 of \citealt{hoyer_tramos_2013}).  However, looking at the I-band
% measurements of \citet{hoyer_tramos_2013} and taking the mean + std
% deviation, it's a ~1 sigma effect. So I won't mention it!
Comparing our empirical result with the Yonsei-Yale evolutionary track
predicted by the spectroscopic parameters, we see that WASP-4 has an
age $\approx 7\,{\rm Gyr}$, and is securely in the main-sequence stage
of evolution.

@@

\begin{figure*}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.9\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Timing residuals and best-fit models for WASP-4b.}
        Points are observed transit times minus a linear fit to all
        observed times.  Less precise times are more transparent.  The
        best constant period model (gray line) is a poor fit to the
        observations.  The best-fit tidal decay model (blue) and
        apsidal precession model (orange) can fit the data.  The
        binned TESS point (red square) is for display purposes only;
        the individual TESS times are used to fit the models.
        \label{fig:times}
    }
\end{figure*}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=0.417\textwidth]{f4.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf WASP-4b should have a short eccentricity damping time and an average
    decay time compared to other hot Jupiters.  It seems to orbit a
    main sequence host.
    }
    {\bf \it Top:}
    Points are transiting giant planets from \citet{bonomo_gaps_2017},
    who measured the eccentricities using radial velocities.  Solid
    squares (including WASP-18b) have significant eccentricity
    detections.  The axes are chosen so that constant eccentricity
    damping timescales (Equation~\ref{eq:de_dt}) are lines.  The
    contours shown assume $Q_{\rm p}' = 10^5$.
    {\bf \it Middle:} 
    Axes are chosen so to that constant orbital decay timescales
    (Equation~\ref{eq:da_dt}) are lines.  The contours shown assume
    $Q_\star' = 10^7$.
    {\bf \it Bottom:}
    HR diagram highlighting WASP-12b, which shows timing variations
    similar to WASP-4b.  We also show hot Jupiters for which we
    detect no timing variation (see \S~\ref{sec:hj_verification}).
    \label{fig:context}
  }
\end{figure}

@@

To explore this possibility, we repeat the timing analysis of the main
paper, for other hot Jupiters with long preceding observing baselines.
We first checked which hot Jupiters were observed over the first two
TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}} and
TEPCat \citep{southworth_homogeneous_2011}.  We then selected hot
Jupiters for which there were at least five distinct epochs reported
in the peer-reviewed literature.  We required that each observation be
of a single transit, that the midpoint be fit as a free parameter, and
that the time system be clearly documented.  Our final hot Jupiter
sample included WASP-4b, 5b, 6b, 18b, and 46b.  The collected and
measured times are given in Tables~5, 6, 7, and 8 for each.

Using the literature timing data for each hot Jupiter, we then
performed a least-squares fit to a linear ephemeris.  Using the
best-fit values and variances, we calculated the precision of the
predicted transit time during the TESS observing epoch.  This gave 11,
94, 18, 42, and 59 seconds for WASP-4b, 5b, 6b, 18b, and 46b.
Comparing the observed and predicted times, Figure~\ref{fig:hjs} shows
that WASP-4b is the only hot Jupiter that transited significantly
earlier than expected.

@@

For each planet, we then ask: what fraction of the posterior for
$t_{\rm offset}$ is consistent with an offset worse than $81.5$
seconds?  For WASP-4b, the answer is unsurpringly about half.  For
WASP-6b, the most constraining object, about 1 sample in 2 million is
consistent with such a timing offset ($4.9\sigma$).  For WASP-18b, 1
in 80 samples would be consistent with this timing offset
($2.2\sigma$), and in WASP-46b, the limit is 1 in 44 samples
($2.0\sigma$).  For WASP-5b, the predicted time is too imprecise to
rule out timing offsets at the necessary amplitude.  Multiplying the
three independent probabilities for WASP-5b, 6b, and 18b, we can rule
out $t_{\rm offset} < -81.5\ {\rm seconds}$ at $6.3\sigma$, or about
about 1 part in 8 billion.

@@

% \section{Verifying the WASP-4 Archival Times}
% \label{sec:verify_archival_times}
% 
% \begin{figure*}[ht!]
%   \begin{center}
%     \leavevmode
%     \includegraphics[width=0.9\textwidth]{f7.pdf}
%   \end{center}
%   \caption{
%     {\bf Extra times for WASP-4b neither confirm nor refute the
%     	period-decay.}
%     Our timing analysis (Section~\ref{sec:timing}) imposes stringent
%     selection criteria for lightcurves.
%     Here we overplot additional points from the Exoplanet Transit
%     Database (ETD), and the discovery epoch from \citet{wilson_wasp-4b_2008}.
%     \label{fig:verify}
%   }
% \end{figure*}
% 
% The preceding analysis shows that the TESS timestamps are consistent
% at the requisite level with the ${\rm BJD}_{\rm TDB}$ reference.
% Another explanation for the WASP-4b timing variation could be
% incorrect archival times.
% As a sanity check on the times we included for our analysis in
% Table~1, we collected times from the Exoplanet Transit Database
% \citep[ETD; ][]{poddany_ETD_2010}.  We considered only the 12
% lightcurves of the highest self-reported quality (${\rm DQ} = 1$).  We
% then inspected each lightcurve by eye.  If the lightcurve showed
% substantial red noise, we discarded it.  This left 9 midtimes,
% reported in ${\rm HJD}_{\rm UTC}$. We converted the times to ${\rm
% BJD}_{\rm TDB}$ \citep{eastman_achieving_2010}.
% 
% The resulting times are shown in Figure \ref{fig:verify}.  Focusing on
% the epochs that overlap with \citet{huitson_gemini_2017}'s study, four
% of six possible times agree with the \citet{huitson_gemini_2017}
% times; the other two fall about 90 seconds early.  With their stated
% uncertainties, these 6 ETD data points are inconsistent with a
% constant period.  The 6 points came from 5 different observers.
% Systematic errors in absolute clock offsets by different observers
% should be uncorrelated; if there were such systematic errors in the
% ETD times, this could explain the many-sigma outliers.  Though the
% majority of the reported times do support the accuracy of the
% \citet{huitson_gemini_2017} times, a systematic procedure would call
% for averaging the ETD times.  If we did this, and discarded the four
% \citet{huitson_gemini_2017} epochs, it is likely that the evidence for
% period decay would become much weaker.  Since
% \citet{huitson_gemini_2017} documented their time system clearly, and
% produced lightcurves of extremely high quality, we included their times
% in our analysis.  From private correspondence with
% \citealt{huitson_gemini_2017}, the authors also stand by their
% timestamps. Since the ETD data come from
% heterogeneous sources, their timestamps are less clearly documented,
% and the times are thus more prone to systematic errors, we
% categorically omit them from consideration.
% 
% We also overplotted the discovery epoch reported by
% \citet{wilson_wasp-4b_2008}. 
% This epoch folded together WASP-S survey data, a partial FTS
% lightcurve, and a complete EulerCam lightcurve. 
% Though not explicitly stated by \citet{wilson_wasp-4b_2008}, the
% archival WASP-S lightcurves are in ${\rm HJD}_{\rm UTC}$, so they can
% be converted to ${\rm BJD}_{\rm TDB}$ without uncertainty in the
% absolute time reference (Collier-Cameron, priv.\ comm.).
% The discovery epoch falls about 2 minutes earlier than the epochs we
% used for the fit, and is visible in the lower left of Figure
% \ref{fig:verify}.
